Corner Localization and Camera Calibration from Imaged Lattices

### 2023-06-12 paper/Chapters/Chapter5.tex
Add presentation, updates

\textbf{OV} \citep{lochmanBabelCalibUniversalApproach2021} is a dataset of
approximately 1400 images. It was collected using eight stereo cameras.
As a calibration pattern, the checkerboard pattern with \(9\times_6\) tags of 22 mm size
was used.

@@

\begin{minipage}{0.5\linewidth}
	To get accurate predictions for the possibly missing points, we need
	very accurate camera calibration. We used the reprojection error as a metric
	for the calibration quality.
	To calculate the reprojection error, we have to perform the
	rootfinding \cref{subsub:back_projection_using_the_division_model}. We assume
	that all of the points lay within the image, or they get out of the borders
	a little bit (we use the constant \(1.1\) of the maximum radius). If the
	camera calibration is poor, the root-finding might fail. On the initial
	calibration the number of failed root-findings was much higher.
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
	\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
				115/Correctly detected,
				80/Reprojection error > 10,
				254/Not correctly detected
			}
		\end{tikzpicture}
	}
	\captionsetup{width=.9\linewidth}
	\captionof{figure}{Initial calibration}
	\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
				658/Correctly detected,
				19/Reprojection error > 10,
				115/Not correctly detected
			}
		\end{tikzpicture}
	}
	\captionsetup{width=.9\linewidth}
	\captionof{figure}{Final calibration}
\end{minipage}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\linewidth}
		\resizebox{\linewidth}{!}{
			\begin{tikzpicture}
				\begin{axis}[
						ybar interval,
						ymin=0,
						ylabel={Frequency},
						xlabel={Value},
						height=0.5\linewidth,
						width=\linewidth,
						ticklabel style = {font=\tiny},
						title={Histogram of points before refinement}
					]
					\addplot+ [hist={data min=0,data max=500,bins=10}] table [y index=0]
						% \addplot+ [hist={bins=30}] table [y index=0]
						{data/occluded_number_of_features.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\linewidth}
		% \centering
		\resizebox{\linewidth}{!}{
			\begin{tikzpicture}
				\begin{axis}[
						ybar interval,
						ymin=0,
						ylabel={Frequency},
						xlabel={Value},
						height=0.5\linewidth,
						width=\linewidth,
						ticklabel style = {font=\tiny},
						title={Histogram of points after refinement}
					]
					\addplot+ [hist={data min=0,data max=500,bins=10}] table [y index=0]
						% \addplot+ [hist={bins=30}] table [y index=0]
						{data/recovered_occluded_number_of_features.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{subfigure}
	\begin{subfigure}[h]{\linewidth}
		\centering
		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
		\caption{Recovered pruned points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{subfigure}
	\hfill
	\caption{Feature refinement on the board with partial board occlusion}
\end{figure}

>>>>

\textbf{OV} \citep{lochmanBabelCalibUniversalApproach2021} is a dataset of
approximately 1400 images. It was collected using eight stereo cameras.
As a calibration pattern, the checkerboard pattern with \(9\times 6\) tags of 22 mm size
was used.

@@

\begin{minipage}{0.5\linewidth}
	To get accurate predictions for the possibly missing points, we need
	very accurate camera calibration. We used the reprojection error as a metric
	for the calibration quality.
	To calculate the reprojection error, we have to perform the
	rootfinding \cref{subsub:back_projection_using_the_division_model}. We assume
	that all of the points lay within the image, or they get out of the borders
	a little bit (we use the constant \(1.1\) of the maximum radius). If the
	camera calibration is poor, the root-finding might fail. On the initial
	calibration the number of failed root-findings was much higher.
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
	\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
				254/Correctly detected,
				80/Reprojection error > 10,
				458/Not correctly detected
			}
		\end{tikzpicture}
	}
	\captionsetup{width=.9\linewidth}
	\captionof{figure}{Initial calibration}
	\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
				658/Correctly detected,
				19/Reprojection error > 10,
				115/Not correctly detected
			}
		\end{tikzpicture}
	}
	\captionsetup{width=.9\linewidth}
	\captionof{figure}{Final calibration}
\end{minipage}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\linewidth}
		\resizebox{\linewidth}{!}{
			\begin{tikzpicture}
				\begin{axis}[
						ybar interval,
						ymin=0,
						ylabel={Frequency},
						xlabel={Value},
						height=0.5\linewidth,
						width=\linewidth,
						ticklabel style = {font=\tiny},
						title={Histogram of points before refinement}
					]
					\addplot+ [hist={data min=0,data max=500,bins=10}] table [y index=0]
						% \addplot+ [hist={bins=30}] table [y index=0]
						{data/occluded_number_of_features.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\linewidth}
		% \centering
		\resizebox{\linewidth}{!}{
			\begin{tikzpicture}
				\begin{axis}[
						ybar interval,
						ymin=0,
						ylabel={Frequency},
						xlabel={Value},
						height=0.5\linewidth,
						width=\linewidth,
						ticklabel style = {font=\tiny},
						title={Histogram of points after refinement}
					]
					\addplot+ [hist={data min=0,data max=500,bins=10}] table [y index=0]
						% \addplot+ [hist={bins=30}] table [y index=0]
						{data/recovered_occluded_number_of_features.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{subfigure}
	\begin{subfigure}[h]{\linewidth}
		\centering
		\includegraphics[width=0.7\linewidth]{refined_overlayed_corners.png}
		\caption{Recovered pruned points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{subfigure}
	\hfill
	\caption{Feature refinement on the board with partial board occlusion}
\end{figure}
